Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-23 longoutput.tex
Apply Chernoff's

\begin{theorem}\label{ThmXZCheck}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$ with  $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	Then there exists an algorithm that accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. This algorithm performs only $X$ and $Z$ measurements on $\ket\phi$, and is classical otherwise.
\end{theorem}
\begin{proof}

	Here we follow \cite{PhysRevA.93.022326}.

	\begin{algorithm}
		\caption{Check for ground state}
		\begin{algorithmic}[1]
			\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
			\State $p_S=\frac{|d_S|}{D}$
			\State $\widetilde{S}\gets$ Pick weighted using $p_S$
			\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
			\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
			\State Accept
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	\begin{align*}
		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
	\end{align*}

@@

\begin{theorem}
	Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
	\begin{itemize}
		\item has $t$ terms
		\item acts on $q$ qubits
		\item Ground state $0$...?
		\item Something something $\frac{3}{4}$?
	\end{itemize}
	Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
	Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Delta$ for $i\ne1$, where $\Delta=\Omega\left(\frac{1}{\poly(t)}\right)$. We now decompose the input in this basis. Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices.
	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
	Fix $\delta<2\Delta$ and partition the multi-indices into three types.
	$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
	$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq 2\delta n}$$
	$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$

	Apply Chernoff bound to $\frac{1}{2}-\delta$. There is overwhelming probability that...
	By Chernoff bound, there is overwhelming probability that...  Then we can write the input (?) as follows.
	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$
	$$c=\sum_{J\in\mathcal{I}_3}\gamma_J\overline{\gamma_J}$$

	Then apply \autoref{ThmXZCheck}. By the linearity of expected values, the number of accepted qubits should be around...

	TODO What about Chernoffs???

>>>>

\begin{algorithm}
	\caption{Check for ground state}
	\label{AlgGroundStateCheck}
	\begin{algorithmic}[1]
		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
		\Procedure{GroundStateCheck}{$\ket\phi$}
		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State $p_S=\frac{|d_S|}{D}$
		\State $\widetilde{S}\gets$ Pick weighted using $p_S$
		\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
		\State Accept
		\Else
		\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{theorem}\label{ThmXZCheck}
	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	Then \autoref{AlgGroundStateCheck} accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$.
\end{theorem}
\begin{proof}

	Here we follow \cite{PhysRevA.93.022326}.
	\begin{align*}
		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
	\end{align*}

@@

\begin{theorem}
	Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
	\begin{itemize}
		\item has $t$ terms
		\item acts on $q$ qubits
		\item Ground state $0$...?
		\item Something something $\frac{3}{4}$?
	\end{itemize}
	Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
	Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Delta$ for $i\ne1$, where $\Delta=\Omega\left(\frac{1}{\poly(t)}\right)$. We now decompose the input in this basis. Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices.
	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
	Fix $\delta<2\Delta$ and let $B=\frac{1}{2}-\delta$. Partition the multi-indices into three types.
	$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
	$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq 2\delta n}$$
	$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$

	Apply \autoref{AlgGroundStateCheck} to every register of $\ket{\phi_1^{\otimes n}}$. By Chernoff bound, there is overwhelming (as $n$ grows) probability that more than $Bn$ registers are accepted. On the other hand, take $J\in\mathcal{I}_3$ and do the same to every register of $\ket{\phi_J}$. By Chernoff bound, there is overwhelming probability that less than $Bn$ registers are accepted.

	Now also define the following.
	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$
	$$c=\sum_{J\in\mathcal{I}_3}\gamma_J\overline{\gamma_J}$$

	Then apply \autoref{ThmXZCheck}. By the linearity of expected values, the number of accepted qubits should be around...
	TODO Does this actually work?
